Mathematical Models of Delta-Notch Signalling

### 2025-03-15 paper/paper.tex
Add linear domain heatmap figure to paper.tex
Added SDE heatmap figure to paper.tex

>>>>

\begin{figure}
  \includegraphics[width=\textwidth]{img/ODEModel_TwoCell_Heatmap.png}
  \caption{Results of the linear domain deterministic ODE model. Heatmap shows Notch levels in each of 8 cells over 1000 time steps.}
\end{figure}

\begin{figure}
  \includegraphics[width=\textwidth]{img/SDE_CellLine_HeatMap.png}
  \caption{Results of the linear domain SDE model. Heatmap shows Notch levels in each of 8 cells over 1000 time steps.}
\end{figure}
